A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-11-08 bioc-workflow.tex
recompile with Lisa's latest ammendments

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Tue Nov  8 16:12:13 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Tue Nov  8 16:12:13 2016 
## Subset [6725,20][5032,20] Tue Nov  8 16:12:14 2016 
## Removed features with more than 0 NAs: Tue Nov  8 16:12:14 2016 
## Dropped featureData's levels Tue Nov  8 16:12:14 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

Another useful visualisation that relies on marker annotation is the
representation of the protein profiles occupancy along the gradient
using the \texttt{plotDist} function. While the PCA plot enables to
efficiently visualise the complete dataset and assess the relative
separation of different sub-cellular niches, comparing profiles of a
few marker clusters is useful to assess how exactly they differ (in
terms of peak channels, for example). On figure \ref{fig:plotDist2},
we plot the profile of the mitochondrial and peroxisome markers to
highlight the differences in profiles between these two sets of
markers along the 6th and 7th channels, as represented above along the
7th PC on the PCA plot on figure \ref{fig:plotmarkers}.

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hlo} \hlkwb{<-} \hlstd{hl[,} \hlkwd{order}\hlstd{(hl}\hlopt{$}\hlstd{Iodixonal.Density)]}
\hlkwd{plotDist}\hlstd{(hlo[}\hlkwd{fData}\hlstd{(hlo)}\hlopt{$}\hlstd{markers} \hlopt{==} \hlstr{"Mitochondrion"}\hlstd{, ],}
         \hlkwc{pcol} \hlstd{=} \hlstr{"purple"}\hlstd{,} \hlkwc{fractions} \hlstd{=} \hlstr{"Fraction.No"}\hlstd{)}
\hlkwd{title}\hlstd{(}\hlkwc{main} \hlstd{=} \hlstr{"Marker occupancy profiles along the gradient"}\hlstd{)}
\hlkwd{matlines}\hlstd{(}\hlkwd{t}\hlstd{(}\hlkwd{exprs}\hlstd{(hlo[}\hlkwd{fData}\hlstd{(hlo)}\hlopt{$}\hlstd{markers} \hlopt{==} \hlstr{"Peroxisome"}\hlstd{, ])),}
         \hlkwc{lty} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"darkblue"}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"l"}\hlstd{)}
\hlkwd{legend}\hlstd{(}\hlstr{"topleft"}\hlstd{,} \hlkwd{c}\hlstd{(}\hlstr{"Mitochondrion"}\hlstd{,} \hlstr{"Peroxisome"}\hlstd{),}
       \hlkwc{lty} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"purple"}\hlstd{,} \hlstr{"blue"}\hlstd{),} \hlkwc{bty} \hlstd{=} \hlstr{"n"}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=.6\textwidth]{figure/plotDist-1}

@@

Direct comparisons of individual channels in replicated experiments
does not provide an adequate, goal-driven assessment of different
experiments. Indeed, due to the nature of the experiment and gradient
fraction collection, the quantitative channels do not correspond to
identical selected fractions along the gradient. As can be seen in the
table below (taken from the \texttt{hl}'s \texttt{pData}, focusing on
channels 7 to 10), different sets of gradient fractions are pooled to
obtain enough material and optimise acurate quantitation.

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Tue Nov  8 16:12:16 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127N &   1 & 127N & 1 to 6 (pooled) & 6.00 \\ 
  X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X128N &   1 & 128N & 10 to 11 (pooled) & 13.30 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
  X128N.1 &   2 & 128N & 10 to 11 (pooled) & 12.50 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

The more relevant comparison unit is not a single channel, but rather
the complete protein occupancy profiles, which are best visualised as
experiment-wide on a PCA plot. As such, we prefer to focus on the
direct, qualitative comparison of individual replicate PCA plots,
assuring that each displays acceptable sub-cellular resolution. Note
that in the code chunk below, we mirror the x-axis to represent the
two figures with the same orientation.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Tue Nov  8 16:12:16 2016 
## Added markers from  'pdres' marker vector. Tue Nov  8 16:12:16 2016 
##  MSnbase version: 2.0.0
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

There are many ways to set thresholds and the choice of method will
depend on the biological question and experimental design at hand. One
viable approach in the frame of the above experimetal design would be
to manually set a FDR, say 5\%, per organelle. To do this the user
would examine the top scoring predictions for each organelle, and then
set a threshold at the score at which they achieve 5\% of false
assignments per organelle.  The definintion of a false assignment
would depend on the information available, for example, validity or
lack of validity for the localisation from another experiment as
reported in the literature or a reliable database.  If such
information is not available, one crude method is to set a threshold
per organelle by extracting the median or 3rd quantile score per
organelle.  For example, in the code chunk below, we use the
\texttt{orgQuants} function to extract the median organelle scores and
then pass these scores to the \texttt{getPrediction} function to
extract the new localisations that meet this scoring criteria. Any
sub-cellular predictions that fall below the specified thresholds are
labelled as unknown.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{)}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4365906               0.3054928               0.3796591 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6956146               0.5986152               0.4308889 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4270518               0.5894672               0.9501479 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7954126               0.7078652               0.3176106 
##         Plasma membrane              Proteasome 
##               0.7149800               0.4148348
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      84                     173                      86 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     296                     476                     100 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      27                     124                     521 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     229                     343                      39 
##         Plasma membrane              Proteasome                 unknown 
##                     319                     158                    2057
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Tue Nov  8 19:46:40 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Tue Nov  8 19:46:40 2016 
## Subset [6725,20][5032,20] Tue Nov  8 19:46:41 2016 
## Removed features with more than 0 NAs: Tue Nov  8 19:46:41 2016 
## Dropped featureData's levels Tue Nov  8 19:46:41 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

Another useful visualisation that relies on marker annotation is the
representation of the protein profiles occupancy along the gradient
using the \texttt{plotDist} function. While the PCA plot enables to
efficiently visualise the complete dataset and assess the relative
separation of different sub-cellular niches, comparing profiles of a
few marker clusters is useful to assess how exactly they differ (in
terms of peak channels, for example). On figure \ref{fig:plotDist2},
we plot the profile of the mitochondrial and peroxisome markers to
highlight the differences in profiles between these two sets of
markers in the channels labelled with tag 129C, as represented above
along the 7th PC on the PCA plot on figure \ref{fig:plotmarkers}.

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hlo} \hlkwb{<-} \hlstd{hl[,} \hlkwd{order}\hlstd{(hl}\hlopt{$}\hlstd{Iodixonal.Density)]}
\hlkwd{plotDist}\hlstd{(hlo[}\hlkwd{fData}\hlstd{(hlo)}\hlopt{$}\hlstd{markers} \hlopt{==} \hlstr{"Mitochondrion"}\hlstd{, ],}
         \hlkwc{pcol} \hlstd{=} \hlstr{"purple"}\hlstd{,} \hlkwc{fractions} \hlstd{=} \hlstr{"Tag"}\hlstd{)}
\hlkwd{title}\hlstd{(}\hlkwc{main} \hlstd{=} \hlstr{"Marker occupancy profiles along the gradient"}\hlstd{)}
\hlkwd{matlines}\hlstd{(}\hlkwd{t}\hlstd{(}\hlkwd{exprs}\hlstd{(hlo[}\hlkwd{fData}\hlstd{(hlo)}\hlopt{$}\hlstd{markers} \hlopt{==} \hlstr{"Peroxisome"}\hlstd{, ])),}
         \hlkwc{lty} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"darkblue"}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"l"}\hlstd{)}
\hlkwd{legend}\hlstd{(}\hlstr{"topleft"}\hlstd{,} \hlkwd{c}\hlstd{(}\hlstr{"Mitochondrion"}\hlstd{,} \hlstr{"Peroxisome"}\hlstd{),}
       \hlkwc{lty} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"purple"}\hlstd{,} \hlstr{"blue"}\hlstd{),} \hlkwc{bty} \hlstd{=} \hlstr{"n"}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=.6\textwidth]{figure/plotDist-1}

@@

Direct comparisons of individual channels in replicated experiments
does not provide an adequate, goal-driven assessment of different
experiments. Indeed, due to the nature of the experiment and gradient
fraction collection, the quantitative channels do not correspond to
identical selected fractions along the gradient. For example, in the
table below (taken from \texttt{hl}'s \texttt{pData}) TMT channels
127C (among others) in both replicates originate from different sets
of gradient fractions (gradient fractions 7 - 9 and 8 - 9 for each
replicate, respectively). Different sets of gradient fractions are
often pooled to obtain enough material and optimise acurate
quantitation.

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Tue Nov  8 19:46:43 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

The more relevant comparison unit is not a single channel, but rather
the complete protein occupancy profiles, which are best visualised 
experiment-wide on a PCA plot. As such, we prefer to focus on the
direct, qualitative comparison of individual replicate PCA plots,
assuring that each displays acceptable sub-cellular resolution. Note
that in the code chunk below, we mirror the x-axis to represent the
two figures with the same orientation.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Tue Nov  8 19:46:42 2016 
## Added markers from  'pdres' marker vector. Tue Nov  8 19:46:43 2016 
##  MSnbase version: 2.0.0
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

There are many ways to set thresholds and the choice of method will
depend on the biological question and experimental design at hand. One
viable approach in the frame of the above experimetal design would be
to manually set a FDR, say 5\%, per organelle. To do this the user
would examine the top scoring predictions for each organelle, and then
set a threshold at the score at which they achieve 5\% of false
assignments per organelle.  The definintion of a false assignment
would depend on the information available, for example, validity or
lack of validity for the localisation from another experiment as
reported in the literature or a reliable database.  If such
information is not available, one crude method is to set a threshold
per organelle by extracting the median or 3rd quantile score per
organelle.  For example, in the code chunk below, we use the
\texttt{orgQuants} function to extract the median organelle scores and
then pass these scores to the \texttt{getPredictions} function to
extract the new localisations that meet this scoring criteria. Any
sub-cellular predictions that fall below the specified thresholds are
labelled as unknown.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{)}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4325847               0.3029421               0.3817418 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6933699               0.6027103               0.4145111 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4276585               0.5845256               0.9490812 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7947588               0.7079465               0.3161762 
##         Plasma membrane              Proteasome 
##               0.7101150               0.4125186
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     172                      84 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     297                     475                      98 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      28                     125                     523 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     228                     343                      38 
##         Plasma membrane              Proteasome                 unknown 
##                     321                     158                    2057
\end{verbatim}
\end{kframe}
\end{knitrout}
